Of judges, aliens and tpos

### 2020-12-30 paper/paper.tex
feat: introduction

% TODO introduction
\section{Introduction}

% goal of paper: interested in function * for getting new tpo

% roten faden des reports beschreiben

@@

\section{Formal background}

@@

\section{Additional metadata for tpo revision}
\subsection{Enriching epistemic states}
Based on DP-AGM and the postulates $(CR1)$-$(CR4)$ Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering. The goal of the paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. These functions are referred to as revision operators for $\leq$.

@@

\section{Booth and Meyer tpo-revision operators}
Booth and Meyer \cite{Booth2011} aim to discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. To do so they define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).

@@

% TODO write Properties of Booth and Meyer tpo-revision operators
\section{Properties of BM tpo-revision operators}
While not determining a concrete operator $\ast_{\preceq}$ to revise a tpo $\leq$, definition \ref{definition:revision-operator} allows Booth and Meyer to discuss what properties any operator in that family must have \cite{Booth2011}.

@@

\section{Iterating: $\preceq$-revision}

The operator $\ast$, based on $\preceq$, allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$. To be used in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}. In their paper they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.

@@

% TODO put examples with alpha: r and alpha p from before here and revise them

@@

@@

% TODO write Discussion
\section{Discussion}
% TODO *6,*7 seem weird, no different "strength" of evidence? maybe revising multiple time by the same evidence should that be? otherwise revising multiple times by same evidence is also weird because it changes things and is not idempotent
% TODO: discuss 6/7 being wrong? strength of evidence?=!=!, discuss 5 with it being equal when sticks - and + are same rank?! 
\newpage

>>>>

\section{Introduction}

In the field of belief change total preorders (or tpos) are a common tool to model an agent's conditional beliefs. To support iterated belief revision it is necessary to research how these structures can be changed to adapt to an agent's changing world view.
Booth and Meyer suggest an approach based on the idea of assigning an interval of additional metadata to the ordered, propositional worlds and iterate the tpo of an agent using that structure. They define and discuss properties of operators for tpo-revision and relate their approach to other fields of research.
This report on their paper aims to present parts of their work to a wider audience with the addition of an accompanying example. The report's focus will be on the tpo-revision operators discussed in the paper and explicitly avoid the addition of strict preference hierarchies and relations to other research areas.
The structure of the report will be as follows: First it will establish the context of the paper by presenting the research area of iterated belief revision and how it relates to other areas of artificial intelligence and philosophy. To establish a shared understanding of notation and definitions section \ref{section:formal-background} will discuss formal background and other, previous approaches to belief change. It will also introduce the main contribution of this report in an accompanying example demonstrating tpo-revision as described by Booth and Meyer. After establishing a foundation, section \ref{section:booth-and-meyer-tpo-revision-operators} and \ref{section:properties-of-bm-tpo-revision-operators} present part of the work from the original paper 'How to Revise a Total Preorder' \cite{Booth2011}. Section \ref{section:booth-and-meyer-tpo-revision-operators} establishes and defines functions $\ast$, used to revise tpos, a core contribution of Booth and Meyer. In section \ref{section:properties-of-bm-tpo-revision-operators} properties of these functions will be presented. To provide an outlook for the additional work done by Booth and Meyer, \ref{section:iterating-preceq-revision} shows their suggestion for a concrete operator for tpo-revision and includes several examples and novel visualisations of it being applied in the context of the accompanying example. Finally section \ref{section:discussion} closes the report with a summary and commentary on Booth and Meyer's approach to iterated belief revision with interval orderings.

@@

\section{Formal background}
\label{section:formal-background}

@@

\section{Additional metadata for tpo revision}
\label{section:additional-metadata-for-tpo-revision}
\subsection{Enriching epistemic states}
Based on DP-AGM and the postulates $(CR1)$-$(CR4)$ Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering. The goal of the paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. These functions are referred to as revision operators for $\leq$.

@@

\section{Booth and Meyer tpo-revision operators}
\label{section:booth-and-meyer-tpo-revision-operators}
Booth and Meyer \cite{Booth2011} aim to discuss tpo revision operators, functions $\ast$ that return a new tpo $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. To do so they define how to use the additional information from a $\leq$-faithful tpo $\preceq$ over $W^{\pm}$ to create a revision operator $\ast_{\preceq}$ (from now on referred to as BM tpo-revision operators).

@@

% TODO write Properties of Booth and Meyer tpo-revision operators
\section{Properties of BM tpo-revision operators}
\label{section:properties-of-bm-tpo-revision-operators}
While not determining a concrete operator $\ast_{\preceq}$ to revise a tpo $\leq$, definition \ref{definition:revision-operator} allows Booth and Meyer to discuss what properties any operator in that family must have \cite{Booth2011}.

@@

\section{Iterating: $\preceq$-revision}
\label{section:iterating-preceq-revision}
The operator $\ast$, based on $\preceq$, allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$. To be used in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}. In their paper they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.

@@

@@

% TODO need this?
\newpage

@@

% TODO write Discussion
\section{Discussion}
\label{section:discussion}
% TODO *6,*7 seem weird, no different "strength" of evidence? maybe revising multiple time by the same evidence should that be? otherwise revising multiple times by same evidence is also weird because it changes things and is not idempotent
% TODO: discuss 6/7 being wrong? strength of evidence?=!=!, discuss 5 with it being equal when sticks - and + are same rank?! 
\newpage
